Meesters TODO List

### 2023-04-19 files/Chapter2/generalvibrationmodel.tex
general vibration problem

Consider Problem GVar defined in Section \ref{ssec:existence:VariationlApproach}. Assume there is no damping and no forcing.

\subsubsection*{Problem GVar}\label{sssec:existence:ProblemGVar}
Find a function $u\in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to $\Vert \cdot \Vert_{W}$ and for each $t\in J,\ u(t)\in V,\ u'(t) \in V,\ u''(t)\in W$ and
\begin{eqnarray}
	c(u''(t),v)+b(u(t),v) = 0 \ \ \ \ \textrm{for each} \ v \in V, \label{eq:existence:ProblemGVarHom}
\end{eqnarray}
with $u(0)=u_{0}$, $u'(0)=u_{1}$.

Consider a trial solution $u(t) = T(t)x$ with $x \in V$ and $x \neq 0$.

>>>>

Consider Problem GVar defined in Section \ref{ssec:existence:VariationlApproach}. In this section, assume there is no damping and no forcing.

\subsubsection*{Problem GVar}\label{sssec:existence:ProblemGVar}
Find a function $u \in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to $\Vert \cdot \Vert_{W}$, and for each $t \in J$, $u(t) \in V$, $u'(t) \in V$, $u''(t) \in W$, satisfying
\begin{eqnarray}
c(u''(t),v)+b(u(t),v) = 0 \ \ \ \ \textrm{for each} \ v \in V, \label{eq:existence:ProblemGVarHom}
\end{eqnarray}
with initial conditions $u(0)=u_{0}$ and $u'(0)=u_{1}$.

To try and find a solution to this problem, consider a trial solution $u(t) = T(t)x$ with $x \in V$ and $x \neq 0$. Substituting this trial solution into \eqref{eq:existence:ProblemGVarHom} results in
\begin{eqnarray*}
	b(T(t)x,v) = - c(T''(t)x,v).  \label{eq:existence:ProblemGVarHom:Substitution}
\end{eqnarray*}

Due to the linearity of the bilinear form, this equation can be rewritten as
\begin{eqnarray*}
	T(t)b(x,v) = - T''(t)c(x,v).
\end{eqnarray*}

Dividing both sides by $T(t)$ gives
\begin{eqnarray*}
	b(x,v) = - \frac{T''(t)}{T(t)}c(x,v).
\end{eqnarray*}

Therefore $\frac{T''(t)}{T(t)}$ must be a constant. Suppose that $\frac{T''(t)}{T(t)} = -\lambda$. The existence of such a $\lambda$ is uncertain at this point. To investigate the existence of such a $\lambda$, consider the following eigenvalue problem.

Find a real number $\lambda$ and a $x \in V$ with $x \neq 0$ such that
\begin{eqnarray*}
	b(x,y) = \lambda c(x,y) \ \ \ \ \textrm{ for each } \ y \in V.
\end{eqnarray*}

A solution to the eigvalue problem consists of an eigenvalue $\lambda$ with corresponding eigenvector $x$.

The article \cite{CVV18} is a convenient reference to show that the eigenvalue problem has a solution if the following assumption is satisfied:

\begin{itemize}
	\item[] \textbf{A5} - The embedding of $V$ into $W$ is compact.
\end{itemize}

(Note that this assumption expands on the assumptions already made in Section 2.2.)

Buidling on assumption \textbf{A5}, the authors of \cite{CVV18} prove that there exists a eigenvalue $\lambda$ and a corresponding eigenvector $x$ such that the eigenvalue problem has a solution. The authors also prove that the eigenvalues are positive, and the corresponding eigenvectors are orthogonal in $W$ (the bilinear form $c$). In fact it is also orthogonal with respect to the bilinear form $b$, hence
\begin{eqnarray*}
	b(x_i, x_j) = \lambda_i c(x_i, x_j) = 0, \ \ \ \ \textrm{ for each } \ i \neq j.
\end{eqnarray*}

The sequence of eigenvalues ${\lambda_i}$ is an infinite sequence with $\lambda_n \rightarrow \infty$ as $n \rightarrow \infty$. The sequence of eigenvectors ${x_i}$ forms an orthogonal basis in $W$, which means that any element of $W$ can be represented as a linear combination of the eigenvectors.

\textcolor{red}{Onseker oor die volgede deel oor die Fourier Coefficients. Moet net nog daaroor dink.}

Following this result, the authors explain that any $u \in V$ can be represented as a linear combination of the eigenvectors $x_i$ with coefficients $a_i$. These coefficients are Fourier coefficients of $u$ with respect to the basis $x_i$. Therefore, for any $u \in V$,
\begin{eqnarray*}
	u = \sum_{i=1}^{\infty} a_i x_i. = \sum_{i=1}^{\infty} c(u, x_i)x_i
\end{eqnarray*}

Now that the eigenvalue problem has a solution, the following ordinary differentiable equation can be considered,
\begin{eqnarray*}
	T'' + \lambda T = 0. 
\end{eqnarray*}

Since this differential equation is a simple second order differential equation, T(t) has the following possible solutions:
\begin{flalign*}
	T_n(t) &= e^{-r_nt}\left[ A_n \cos(\omega_n t) + B_n \sin(\omega_n t) \right],\\
	T_n(t) &= e^{-r_nt}\left[ A_n + B_n t) \right],\\
	T_n(t) &= e^{-r_nt}\left[ A_n \cosh(\mu_n t) + B_n \sinh(\mu_n t) \right].
\end{flalign*}

***********************************************
